Nonparametric Spectral Siren Cosmology

### 2023-10-06 src/tex/ms.tex
[showyourwork] overleaf sync

\section{Introduction}
\label{sec:intro}
Like light, gravitational waves (GWs) are redshifted as they propagate across the universe.
Unlike light, however, the selection effects of GWs are extremely well understood, allowing for a precise estimate of each catalogs’ completeness and an unbiased measurement of the true GW population.
This allows GW signals to be used as relatively clean probes of cosmological parameters \citep[e.g.][]{bright sirens first paper, 170817 bright siren, dark siren first paper, dark siren with 0817, hithhikers guide}.

GW signals provide direct measurements of each source’s luminosity distance and redshifted, or detector frame, masses, $m_{\det} = m_{\source}(1+z)$.
Therefore, if the source frame mass is known, each event provides a direct mapping between luminosity distance and redshift, allowing for a measurement of the rate of expansion of the universe at the time the GW signal was emitted, $H(z)$.
In practice, the source frame mass is unknown, but it is possible to know the location of features in the source frame mass distribution.
The whole mass distribution therefore acts similarly to an electromagnetic spectrum, where the location of spectral features provides a redshift measurement.
The method of using the mass distribution of GW sources to measure cosmological parameters has therefore been coined ``spectral sirens'' \citep{ezquiaga_spectral_2022}.
Spectral sirens were first demonstrated to be a feasible method to measure the Hubble constant by \cite{chernoff+fin} using the BNS mass distribution, and extended to the BBH mass distribution by \cite{farr_future_2019}.

>>>>

\section{Introduction}
\label{sec:intro}
Like light, gravitational waves (GWs) are redshifted as they propagate across the universe.
Unlike light, however, the selection effects of GWs are extremely well understood, allowing for a precise estimate of each catalogs' completeness and an unbiased measurement of the true GW population.
This allows GW signals to be used as relatively clean probes of cosmological parameters \citep[e.g.][]{bright sirens first paper, 170817 bright siren, dark siren first paper, dark siren with 0817, hithhikers guide}.

GW signals provide direct measurements of each source's luminosity distance and redshifted, or detector frame, masses, $m_{\det} = m_{\source}(1+z)$.
Therefore, if the source frame mass is known, each event provides a direct mapping between luminosity distance and redshift, allowing for a measurement of the rate of expansion of the universe at the time the GW signal was emitted, $H(z)$.
In practice, the source frame mass is unknown, but it is possible to know the location of features in the source frame mass distribution.
The whole mass distribution therefore acts similarly to an electromagnetic spectrum, where the location of spectral features provides a redshift measurement.
The method of using the mass distribution of GW sources to measure cosmological parameters has therefore been coined ``spectral sirens'' \citep{ezquiaga_spectral_2022}.
Spectral sirens were first demonstrated to be a feasible method to measure the Hubble constant by \cite{chernoff+fin} using the BNS mass distribution, and extended to the BBH mass distribution by \cite{farr_future_2019}.
